### 2014-03-07 src/analysis.Rnw
update

\section{Analysis}
\label{sec:analysis}

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

@@

>>>>

\section{Analysis}
\label{sec:analysis}
\begin{figure*}[!htb]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

@@

First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
This provided us with the relative number of each mutation operators, that are produced, and also the general number of
mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}.
